---
title: blog-2017-11-13-wordcloud
author: HLB
date: '2017-11-13'
slug: blog-2017-11-13-wordcloud
categories:
  - R
tags:
  - bing
  - Dracula
  - gutenbergr
  - sentiments
  - text mining
  - tidytext
  - reshape2
  - wordcloud

summary: Creating a wordcloud & wordcloud 2 with tidy text, sentiment words and text mining in gutenbergr.
---

We are still working with text mining.  Today we are going to create a wordcloud using the positive & negative sentiments mined from the text. 

Just as always, we begin my loading (and library) the packages that we'll use today: dplyr, gutenbergr, tidytext, tm (don't have to library), wordcloud & (new) wordcloud2 & (also new) reshape2.
```{r message=FALSE,warning=FALSE}
library(dplyr)
library(gutenbergr)
library(tidytext)
library(tm)
library(wordcloud)
library(wordcloud2)
library(reshape2)
```

Now we need some text; we'll download the novel Dracula from gutenbergr we've been working with this for a while & we know the download # is 345.
```{r}
dracula<-gutenberg_download(345)
```

Then we will 'unpack' the text column by unnesting the tokens with tidy text to get the words in Dracula.  We'll save this to a data frame Dracula_words.
```{r}
dracula_words<-dracula%>%
  unnest_tokens(word,text)
```

We aren't going to worry about the stop words (a, an, the, etc.) because we are going to work with 'bing' to rate the words as positive or negative.
```{r}
bing<-get_sentiments('bing')

```
We'll look at the data frame for dracula_words  & bing.
```{r}
dracula_words

bing
```
Dracula Words has 3 columns:  the line number, Gutenberg id number & the word. Bing is the list of words & the sentiment attached to each word as positive or negative.
We'll join the Dracula words & bing together.

```{r}
dracula_words<-inner_join(dracula_words,bing)
head(dracula_words)
```

Now we have 4 columns: the line number, Gutenberg id number, the word & the sentiment.
We don't need the Gutenberg id number column so we'll get rid of that with NULL.
```{r}
dracula_words$gutenberg_id<-NULL
head(dracula_words)

```

We now have the information we want to make a word cloud. 

#Wordcloud

To get a wordcloud, we need to group the words & count by the sentiment.  We'll use freq(frequency) for n (rather than count.  

```{r}
dracula_words<-dracula_words%>%
  group_by(word)%>%
  summarize(freq=n(),sentiment=first(sentiment))
```

Now a simple wordcloud:
We'll have to add the "message=FALSE,warning=FALSE" to supress error messages because some of the word's won't fit.

```{r message=FALSE,warning=FALSE}
wordcloud(dracula_words$word, dracula_words$freq,min.freq = 11)
```

Now let's try wordcloud2, the new package we installed for today.  For wordcloud 2 we need ca column for word & a column frequency (freq).

#wordcloud2

```{r message=FALSE,warning=FALSE}
wordcloud2(dracula_words)
```

Very simple code & the result is in <strong>color</strong>.
We can even specify the background color:

```{r message=FALSE,warning=FALSE}
wordcloud2(dracula_words,background ='black')
```

The other new package we installed is reshape2.  This allows us to get a comparison wordcoud. 
We need to change our data frame into a matrix.  The 'word' column becomes our 'row' with each word representing a row & then we add/create 2 columns ('negative & positive').  
We don't want to see an 'NA' in our matrix so we need to make the NA 0 (zero)
fill = 0 is for Na to be 0
There will be a 0 (zero) in the positive column for negative words & a 0 (zero) in the negative column for positive words.
The code is: "acast(dracula_words,word~sentiment,value.var='freq',fill =0)"

We'll save this into a variable dracula_matrix & look at the head.
```{r}
dracula_matrix<-acast(dracula_words,word~sentiment,value.var='freq',fill =0)
head(dracula_matrix)
```

We see the word and then a negative and positive column.  The totals for each word are summed in these columns.

With wordcloud2 the comparison cloud is easy to code: 

```{r message=FALSE,warning=FALSE}
comparison.cloud(dracula_matrix)
```

The positive & negative are in different colors.  We can choose our own colors using colors=c(('black', 'orange').  We can use the htmlcolor codes that we find on the web too

```{r message=FALSE,warning=FALSE}
comparison.cloud(dracula_matrix,colors=c('black', 'orange'))
```

Now our positive sentiments are orange & our negative sentiments are black.

#Using Wordcloud 2 to 'shape' our cloud

Go out to google & find some clipart.  Since this is a Halloween theme, we'll look for a bat.  When we google 'free clip art bat" Download the .jpg, .gif, or .png file the clipart & put it in your working directory with your R script document.
For the blog, we'll need to save it to our images in the image folder.

Then we just add fig='filename.jpg' & it will shape the cloud.

```{r message=FALSE,warning=FALSE}
wordcloud2(dracula_words,fig='bat2.jpg')
```

We can use a different clip art, add a size & the background color too.
```{r message=FALSE,warning=FALSE}
wordcloud2(dracula_words,fig='bats3.gif', background='black')
```





fin-ne