---
title: Blog 2017-09-25 Data Visualization Bar Graph
author: Hbeezub
date: '2017-09-25'

tags:
  - Data650
  - Data Visualization
  - Rstudio
  - ggplot
  - bar graph
  
summary: Data Visualization Bar Graph example in R-studio (9-25)
---

What else I learned note: Important, when creating a blog, don't try to copy in info from a word document (the Rmarkdown file doesn't like it).  You'll only have to scrap what you've done & start over.

So now let's explore a bar chart.

As with any r-studio project we will need to install packages & then load libraries.
In R-studio go to tools (at the top menu bar) click on "install packages".  Type devtool in the pop up box and click on install button.
Repeat installation for Lahman, dplyr, ggplot, and ggiraph.  To install blogdown.
Then bring in the libraries for devtools, Lahman, dplyr, ggplot, and ggiraph.

```{r warning=FALSE, message=FALSE}
library(devtools)
library(Lahman)
library(dplyr)
library(ggplot2)
library(ggiraph)
```

Now we need some data.  How about the total team Home Runs from 1980. The summer of 1980 I had just finished my Freshman year of High School; I was officially a Sophmore (ie wise fool).

```{r}
df<-Teams%>%
  filter(yearID==1980)%>%
  select(name,HR)
```

As in our scatter plot (previous post) we've defined our data with "df<-".  The "%>%"" is a continuation character.

The basic graph is next.  With the bar chart we need to add "stat='identity'":

```{r}
ggplot()+
  geom_bar(data=df,aes(x=name,y=HR),stat="identity")
```


#Whoa
Well, we have a graph, but we can't read the team names on the bottom.  We need to flip the axis.

```{r}
ggplot()+
  geom_bar(data=df,aes(x=name,y=HR),stat="identity")+
  coord_flip()
```

<strong>Much Better</strong>
Now, I really can't tell (easily) if the Astros had more Home Runs than the  Padres.  What we need to do is to put these in order. 

Simply, adding "arrange" to the dplyr code for our base data didn't work.  So what we need to do is add in a factor.  

```{r}
df<-Teams%>%
  filter(yearID==1980)%>%
  select(name,HR)%>%
  arrange(HR)
df$name<-factor(df$name,levels=df$name)
ggplot()+
  geom_bar(data=df,aes(x=name,y=HR),stat="identity")+
  coord_flip()
```

#Now we're cooking with gas

Ok let's add some color and we're done:

```{r}
df<-Teams%>%
  filter(yearID==1980)%>%
  select(name,HR)%>%
  arrange(HR)
df$name<-factor(df$name,levels=df$name)
ggplot()+
  geom_bar(data=df,aes(x=name,y=HR),stat="identity",color="blue",fill="white")+
  coord_flip()
```

end