---
title: Blog 2017-09-24 Data Visualization (blog#2.4)
author: Hbeezub
date: '2017-09-24'

tags:
  - Data650
  - Data Visualization
  - Rstudio
  - ggplot
  
summary: Data Visualization example in R-studio (9-22)version 2.0
---

OK so this is attempt 4 for this blog post.  So my AHa shower moment was "I'm using the wrong file format."  Sure enough, I was using an ".md" file, but I needed a ".Rmd" file.  Ok so then I was still having issues (well, I have issues so let's clarify-issues with the site giving me an error when I tried to build it).  So copy someone elses work & make changes so that it fits your original intent (& it isn't plagiarism -btw-thank's Jorge).  So now we're cooking with gas.  I can get rid of the info I don't understand & add things like summary & the site will <strong> build. </strong> Yes & I figured out (on my own) how to get that "build" bold).

The text is the same, but this time I have the code inserted that I want.

We used R-studio to create a scatter plot of baseball information (from the Lahman library).  Aside from learning how to do the scatter plot, the most interesting thing I learned is that the "css" that I keep seeing in the sample blog has to do with viewing the HTML information.  I had been wondering what all of them were (and now I know)

I. Our first step was to open r-studio and install all the packages we would need and then bring them all in with 'library':

```{r warning=FALSE, message=FALSE}
library(devtools)
library(Lahman)
library(dplyr)
library(ggplot2)
library(ggiraph)
```

II. We pulled some interesting information: players with more than 400 career Home runs, but we also wanted to know the number of strikeouts too.  We used the following code:

```{r}
df<-Batting %>%
  group_by(playerID)%>%
  summarize(career_HR=sum(HR), career_SO=sum(SO))%>%
  filter(career_HR >=400)
```

III. We then created our graph using ggplot, in the same way that the '%>%' is the continuation character for r markdown, the '+' is the continuation character for  ggplot.  the 'aes' (asthetic) is for the xy axis.  The geom_point indicates we want a scatter plot (points).  If we wanted some other type, like a bar chart we would use geom_bar.  ggtitle gives our graph it's name, and the xlab & ylab (label) give the axes names.

```{r}
HR_vs_SO<-inner_join(df,Master,by=c("playerID"))%>%
  select(nameFirst,nameLast,career_HR,career_SO)

g<-ggplot()+
  geom_point_interactive(data=HR_vs_SO,aes(x=career_SO,y=career_HR))+
  ggtitle("Career Home Runs vs Strike Outs for Great Hitlers.")+
  xlab("Career Strikeouts")+
  ylab("Career Homeruns")

```

Again we want to 'save' this so we name it (like we did the batting information) 'g<-' before ggplot.

This gives us a nice visual, but we don't know what (or rather who) the points represent.

IV. So we use colnames(master) to find out the table names in the Lahman information.  Now we want to 'paste' together the first & last names.  The following code is added to the 'Batting' code to show the first & last names:

```{r}
HR_vs_SO<-inner_join(df,Master,by=c('playerID'))%>%
  select(nameFirst,nameLast,career_HR,career_SO)

```

'V.' Now we add a little more code we define the name as a tool tip & modify our gg plot code so that as we hover over our points, we get the names:

geom_point_interactive(data=HR_vs_SO,aes(x=career_SO,y=career_HR,tooltip=name, data_id=nameLast))

and add some color to our visual:

ggiraph(code=print(g),hover_css="Fill:white;stroke:blue")

VI.Ok, so the final code looks like this:

```{r}
df<-Batting%>%
  group_by(playerID)%>%
  summarize(career_HR=sum(HR),career_SO=sum(SO))%>%
  filter(career_HR >= 400)

HR_vs_SO<-inner_join(df,Master,by=c("playerID"))%>%
  select(nameFirst,nameLast,career_HR,career_SO)

HR_vs_SO$name<-paste(HR_vs_SO$nameFirst,HR_vs_SO$nameLast)

g<-ggplot()+
  geom_point_interactive(data=HR_vs_SO,aes(x=career_SO,y=career_HR,tooltip=nameLast,data_id=nameLast))+
  ggtitle("Career Home Runs vs Strike Outs for Great Hitlers.")+
  xlab("Career Strikeouts")+
  ylab("Career Homeruns")

ggiraph(code=print(g),hover_css="Fill:white;stroke:blue")
```

