---
title: Blog 2017-09-27 Data Visualization Bar Graph round 2
author: Hbeezub
date: '2017-09-27'

tags:
  - Data650
  - Data Visualization
  - Rstudio
  - ggplot
  - bar graph
  - factor
  - class
  
summary: Data Visualization Bar Graph more info (9-27)
---

Let's revisit our prior 9-25 post on bar graphs.  We will talk a little bit about varaible types.  First we need to install packages & load libraries (just like our previous posts):

```{r warning=FALSE, message=FALSE}
library(devtools)
library(Lahman)
library(dplyr)
library(ggplot2)
library(ggiraph)
```

So when we look at our prior code, we defines a variable called 'df$name.'
What we want to find out is what type variable it is.

```{r}
df<-Teams%>%
  filter(yearID==1980)%>%
  select(name,HR)%>%
  arrange(HR)
df$name<-factor(df$name,levels=df$name)
```

if we type "Teams" into the r studio command line it retuens the information in the table "teams."
if we trple class(Teams) it returns the "type" [1] "data.frame" telling us it is a data frame.

if we type "class(df$name)" into r studio is retuns [1} "factor" as the variable type

factors have levels.
again if we type "factor(df$name)" into the Rstudio command line it returns the names of the 25 teams & ends with "26 Levels: New York Mets San Diego Padres ... Milwaukee Brewers"  Telling us tehre are 26 levels in the factor.

What all this tels us is that we can modify & control the types of variables.  

end
